\documentclass[a4paper]{norm-resume}

\usepackage{array}
\usepackage{tabularx}
\usepackage{setspace}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\pagenumbering{gobble}

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ayush}{Tulsyan}{}{Email: ayusht@iitk.ac.in, Phone: +91-727-552-8595}

\vspace{3mm}

% Education section : With current and previous schooling

\section{Education \hrulefill}

\begin{tabularx}{\textwidth}{c l l r}
    {April 2018 \hspace{10mm}} & B.Tech \emphasize{(Computer Science And Engineering)} \hspace{20mm} & \emphasize{IIT Kanpur \hspace{7mm}} & {\textbf{{7.5/10.0}}}\\
    {April 2014 \hspace{10mm}} & Class XII \emphasize{(Central Board for Senior Education)} & \emphasize{B.P.S. Burhanpur} & {\textbf{{89.60 \%}}}\\
    {April 2012 \hspace{10mm}} & Class X \emphasize{(Central Board for Senior Education)} & \emphasize{N.M.S.S. Burhanpur} & {\textbf{{10.0/10.0}}}\\
\end{tabularx}

\vspace{2mm}    % Some space before next section

% Academic Achievements

\section{Academic Achievements \hrulefill}

\vspace{5mm} %Some space

\begin{tightitemize}
    \item Secured AIR - \textbf{197} in {\textbf{JEE (Advanced) 2014}} among 125K Candidates
    \item Secured \textbf{KVPY} Scholarship 2014 under stream SX with a rank of \textbf{226}
    \item Secured \textbf{99.97 percentile in JEE Mains 2014} Test among 1.5 Million Candidates
    \item Received \textbf{A* grade} for exceptional performance in \textbf{Data Structures and Algorithms} course.
    \item Amongst top 300 students qualified for \textbf{Indian National Astronomy Olympiad 2014} conducted by \textbf{HBCSE}.
\end{tightitemize}

% Details about the projects

\section{Internship \hrulefill}

\vspace{2mm} %Some space
    \runsubsection{Summer Analyst}  \descript{May '17 - July '17}
    \emph{Goldman Sachs Services Pvt Ltd, Bengaluru: Data Architecture Team in Technology Division}
    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item Explored the possibility of \textbf{SQL-on-Hadoop} replacing the current data warehousing solution used by the Enterprise. Specifically focussed on \textbf{Presto}, which is an open source \textbf{distributed SQL query engine} primarily used for processing \textit{Big Data}
    \item Evaluated Presto against \textbf{Sybase IQ} through comparing them using queries, guidelines, and dataset provided by \textbf{TPC-DS Benchmark}, while \textit{assimilating the enterprise's context} by adding frequently used queries, UDFs, and datatypes to query set
    \item Automated the process of \textit{data generation, migration, creating tables and indices, query execution and recording of evaluation time} in conditions which include variation in \textit{scale of data, number of concurrent users and resource available for computation}
    \item Presented \textbf{comprehensive analysis} of factors contributing to decision of deploying Presto to \textbf{four MDs from GS's New York Office}
    }
    \end{tightitemize}

% Details about the projects

\section{Projects \hrulefill}

\vspace{2mm} %Some space
    \runsubsection{Java to MIPS Compiler:}  \descript{Jan '17 - April '17}
    \emph{Course Project for course CS335A: Compiler Design, under Prof. Amey Karkare} \hfill \small \href{https://github.com/vtantia/java-compiler}{Github}
    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item An end-to-end compiler in Python for a subset of Java Language to produce instructions in MIPS Assembly
    \item Implemented a parser using Python Lex and Yacc (PLY) to build symbol table, check syntax errors and suggest changes.
    \item Incorporated support for recursion, dynamic memory allocation, multi-dimensional arrays and preliminary OOP.
    }
    \end{tightitemize}

    \vspace{5mm}

    \runsubsection{RailQuery:}  \descript{Jan '17 - April '17}
    \emph{Course Project for course CS315A: Principles of Database Systems, under Prof. Medha Atre} \hfill \small \href{https://github.com/ayush-tulsyan/RailQuery}{Github}
    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item Implemented an ANNE(Angular, NodeJS, Neo4J, Express) stack based railway enquiry platform using graph based database
    \item Designed the graph structure to improvise query response time on standard queries like train between stations, connecting trains and fetching train route. Further fine tuned it for a seamless user experience by incorporating indices.
    }
    \end{tightitemize}

    \vspace{5mm}

    \runsubsection{NachOS Operating System:}   \descript{July '16 - Nov '16}
    \emph{Course Project for course CS330A: Operating Systems, under Prof. Mainak Chaudhuri} \hfill \small \href{https://github.com/sakshamsharma/cs330assignments}{Github}
    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item \textbf{Extended} the \textbf{NachOS} operating system to perform basic operating system functions including \textbf{Fork, Join, Sleep, Exec} and \textbf{Exit}.
    \item Implemented and evaluated performance of various algorithms for scheduling processes including \textbf{Non-Preemptive FCFS, Shortest Job First, Pre-emptive Round Robin} and \textbf{UNIX Scheduling}.
    \item Implemented Shared Memory Allocation, \textbf{Demand Paging} and Page Replacement Algorithms including \textbf{FIFO, LRU and LRU-Clock} and analyzed their performance.
    }
    \end{tightitemize}

    \vspace{5mm}

    \runsubsection{BAJA SAE, IITK Motorsports:}	\descript{Jan '15 - Jan '16}
    \emph{Faculty Advisor: Prof. Avinash Kumar Agarwal, Dept of Mechanical Engineering} \hfill \small \href{https://ayush-tulsyan.github.io/files/projects/B16ChassisDesignReport.pdf}{Report}
    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item Amongst the 24 members of the team who worked on a \textbf{yearlong project} which involved \textbf{designing and manufacturing} an \textbf{All-Terrain Vehicle} and competed in \textbf{Baja Student India ’16}, held in Noida in Jan ’16.
    \item \textbf{Lead the Chassis subsystem} during the designing phase of \textbf{3 months during summer}. \textbf{Optimized the strength and weight} of the roll cage by \textbf{virtual designing and simulation}. Intensively simulated the CAD Model for ensuring the \textbf{reliability of structure and safety of driver}.
    }
    \item The Team stood 13\textsuperscript{th} in Overall ranking, 6\textsuperscript{th} in the Design event, 4\textsuperscript{th} in both Acceleration and Maneuverability event.
    \end{tightitemize}

    \vspace{5mm}

    \runsubsection{Other Minor Projects:}

    \vspace{3mm}
    \begin{tightitemize}
    \small
    {
    \item \textbf{Identifying Vulnerabilities and Secured Zoobar Application:} Identified potential exploitable vulnerabilities in web server including buffer overflow, Phishing, Cross Site Request Forgery, Profile Worms, Password theft. Improved application's security using separate process for different services, jailed processes and user/group permissions.
    \item Made a \textbf{html and a proxy server} for GET requests in C++ as a project under Course \textbf{Computer Networks} using a Parsing Library.
    \item Analyzed and Suggested Improvements for \textbf{Stable Marriage Algorithm} as a project in course \textbf{Discreet Mathematics} under Prof. Rajat Mittal. \hfill \href{https://ayush-tulsyan.github.io/files/projects/CS201ProjectReport.pdf}{Report}
    }
    \end{tightitemize}

\vspace{2mm}    % Some space before next section

% Programming Achievements

\section{Achievements in Programming \hrulefill}

\vspace{2mm} %Some space

\begin{tightitemize}
    \small
    {
    \item Secured Rank \textbf{25\textsuperscript{th}} in \textbf{ACM-ICPC Chennai Onsite 2016} among 120 teams and Rank \textbf{50\textsuperscript{th}} in \textbf{Amritapuri Onsite 2016} among 391 teams shortlisted through previous rounds and then further qualified for \textbf{ICPC India-Final 2016}
    \item Secured Rank \textbf{46\textsuperscript{th}} in \textbf{ACM-ICPC India Regionals, Online round 2016} among 3000 teams from over the country.
    \item Secured Rank \textbf{221\textsuperscript{th}} in \textbf{Snackdown 2017 Online Elimination} among 3400 teams selected among 24000 teams.
    \item Secured Rank \textbf{304\textsuperscript{th}} in \textbf{Snackdown 2016 Online Elimination} among 3600 teams selected among 13000 teams.
    % \item \textbf{Expert} level participant on Codeforces in Live contests. (Handle: Tulsyan)
    \item Best Ranked 212 internationally among 8400 people in Codeforces Round 360 Div 2.
    \item Rating of 8402.38 for long contests on Codechef. (10 days long monthly programming contests)
    \item Achieved an overall rating of 2122 points on Codechef, thus being classified as a 5 star contestant.
    }
\end{tightitemize}

% Positions of Responsibility

\section{Positions of Responsibility \hrulefill}

    \begin{tabular}{r|p{16cm}}

    \normalsize\emph{Feb '16 - July '16} & \normalsize\textbf{Subsystem Head, Chassis, IITK Motorsports}\\
    \normalsize\emph{Apr '15 - Apr '16} & \normalsize\textbf{Academic Mentor (ESC101A), Counselling Service}\\
    \normalsize\emph{Jun '15 - Apr '16} & \normalsize\textbf{Student Guide, Counselling Service}
    \end{tabular}

\vspace{2mm}    % Some space before next section

% Skills

\section{Technical Skills \hrulefill}

\vspace{2mm}

\category{\normalsize{Programming Languages}} \hfill \emphasize{C, C++, Python, Bash} \\
\category{\normalsize{Programming Languages} \small\scshape(Familiar):} \hfill \emphasize{Java, HTML, CSS, JavaScript, PHP, MatLab, Verilog, Assembly} \\
\category{\normalsize{Software and Utilities:}} \hfill \emphasize{Git, \LaTeX\, Linux Shell Utilities}

\vspace{2mm}    % Some space before next section

% Relevant Courses

\section{Relevant Courses \hrulefill}

\vspace{2mm}

    \begin{tabular}{lp{15cm}}

	\normalsize\emph{Computer Science:} & \small{Randomized Algorithms, Design and Analysis of Algorithms, Operating Systems, Compilers, Computer Systems Security, Computer Networks*, Machine Learning Techniques*, Visual Recognition*, Data Structures \& Algorithms, Theory of Computation, Computer Organization, Database Systems, Computing Laboratory – I \& II} \\
	\normalsize\emph{Others:} & \small{Discrete Mathematics, Linear Algebra \& Ordinary Differential Equations, Analytical Calculus, Abstract Algebra, Intro to Logic, Probability \& Statistics, Electronics, Intro to Biotechnology, Development Economics}
    \end{tabular}

\vspace{2mm}    % Some space before next section

% Extra Curricular

\section{Extra-Curricular Activities \hrulefill}
\vspace{2mm}

    Competed in \textbf{Code.Fun.Do 2015} and made an application which intends to smoothen out \textbf{document handling}. \\
    Designed a Website for Institute’s SAE team. \\
    Member of team which received Best Sectional Project Award in course project of Manufacturing Processes(TA201A)
\end{document}
